Using Genetic Algorithms to Optimize the Analogue Method for Precipitation Downscaling in the Swiss Alps

### 2016-02-08 Optimization case study - Journal of Hydrology/elsarticle-template.tex
Moving tables at the end of the document.
Personal corrections.

\begin{abstract}
The analogue method is often used to forecast precipitation based on predictors variables provided by global models. The method samples a selection of days in the archives that are similar to the target day to forecast, and consider the set of their corresponding observed precipitation (the predictand) as the conditional distribution for the target day. The relationship between predictors and predictands relies on some parameters that characterize how and where the similitude between two atmospheric situations is defined.

@@

With the perspective to overcome these limitations, a global optimization by Genetic Algorithms (GAs) was introduced by \citet{Horton2016a}. An intensive assessment work resulted in recommendations of parametrization of GAs in order to optimize AMs successfully. The present paper is based on these recommendations and illustrate them on precipitation forecasting for the upper Rh\^{o}ne catchment in the Swiss Alps. It aims at proving the relevance of a fully-automatic, objective, and global, optimization technique for AMs. The applications are indeed numerous, as the AM has to be adapted to every new location it is applied, or to any new predictand it should forecast.

@@

\begin{table}[htb]
	\caption{Parameters of the reference method on the atmospheric circulation (2Z). The first column is the level of analogy (0 for preselection), then comes the meteorological variable and its hour of observation (temporal window). The criteria used for the current level of analogy is then provided, as well as the number of analogues.}
	\footnotesize
	\begin{center}
		\begin{tabular}{ccccc}
			\hline
			Level & Variable & Hour & Criteria & Nb \\ 
			\hline 
			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
			\hline 
			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
			& Z500 & 24~h & & \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:params_R1}
\end{table}

@@

\begin{table}[htb]
	\caption{Parameters of the reference method with moisture variables (2Z-2MI). Same conventions as Table \ref{table:params_R1}}
	\footnotesize
	\begin{center}
		\begin{tabular}{ccccc}
			\hline 
			Level & Variable & Hour & Criteria & Nb \\ 
			\hline 
			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
			\hline 
			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
			& Z500 & 24~h & & \\ 
			\hline
			\multirow{2}{*}{2} & TPW * RH850 & 12~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{30} \\
			& TPW * RH850 & 24~h & & \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:params_R2}
\end{table}

@@

The AM relies on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series one wants to forecast.

@@

The score that is most often used to assess an AM performance is the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}. It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analogue situations, compared to the observed value $y^{0}$. The better the forecast, the smaller the score. The mean CRPS of a forecast series of length $n$ can be written:

@@

\begin{equation}
\label{eq:CRPSS}
CRPSS = \frac{CRPS-CRPS_{r}}{CRPS_{p}-CRPS_{r}} = 1-\frac{CRPS}{CRPS_{r}}
\end{equation}
where $CRPS_{r}$ is the CRPS value for the reference and $CRPS_{p}$ would be the one for a perfect forecast (which implies $CRPS_{p}~=~0$). A better forecast is characterized by an increase in CRPSS.

@@

The reference method for the analogy of the atmospheric circulation (2Z, Table \ref{table:params_R1}), based on the 500 and 1000~hPa levels, was first considered. The optimizer had to choose the number of analogues, both spatial windows with no overlapping constraint, as well as the temporal windows (hours of observation of the geopotential), what the sequential calibration cannot do. With these degrees of freedom, a relative CRPSS improvement of 3.97\% and 2.45\% in average was obtained for the CP and the VP respectively. Some tests showed that most of the gains are due to the non-overlapping spatial windows. This is not a tremendous improvement, but it demonstrated that the optimizer was able to get relevant parameters.

Then, an additional degree of freedom was provided to the GAs by letting them choose the pressure levels along with the other parameters, which is also a non-automated process in the sequential calibration. This degree of freedom increased the optimization time and may decrease the number of simulations that converge to a single solution. However, most solutions were very close in terms of score. The averaged relative improvement of the CRPSS is 5.63\% for the CP and 3.82\% for the VP. The pressure levels that were chosen are 500~hPa or 700~hPa for the upper level, and 925~hPa or 1000~hPa (most often) for the lower level.

Parallel analyses showed that the analogy of circulation is incomplete, and that the geopotential still contains relevant information that can improve the statistical relationship. Therefore, a third predictor was added (still on the geopotential height) that the optimizer could use along with the previous parameters. There was no constraint on the predictors, so that the same pressure level could be selected more than once. Some improvements were found on the score, both for the CP and the VP, confirming that this additional information is beneficial for the quality of the forecast. We then tried with 4 predictors, and so on, up to 8. Every time a new predictor to optimize was added, the score on the CP increased, but always more to a smaller extent. However, the score value on the VP dropped after 4 predictors, revealing an over-parametrization of the method, and thus a lack of robustness. Considering 4 predictors is optimal for this case study, since the gain in CRPSS is significant. It cannot be excluded that another number would prevail in another region under other meteorological conditions.

@@

\begin{table}[htb]
	\caption{Parameters of the 4Zo method (analogy on 4 levels of the atmospheric circulation) optimized for the Chablais subregion. The columns are the following: L = level of analogy, V = meteorological variable, H = hour of observation or temporal window, D = domain or spatial window, W = weighting of the score for the selected pressure levels, C = criteria, N = number of analogues.}
	\footnotesize
	\begin{center}
		\begin{tabular}{ccccccc}
			\hline L & V & H & D & W & C & N \\ 
			\hline 
			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
			\hline 
			\multirow{8}{*}{1} &  \multirow{2}{*}{Z300} & \multirow{2}{*}{12~h} & -2.5 - 15.0 \degree E & \multirow{2}{*}{32\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{28} \\
			& & & 37.5 - 57.5 \degree N & & & \\ 
			& \multirow{2}{*}{Z700} & \multirow{2}{*}{24~h} & 2.5 - 10.0 \degree E & \multirow{2}{*}{22\%} & & \\ 
			& & & 42.5 - 45.0 \degree N & & & \\ 
			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{6~h} & -5.0 - 15.0 \degree E & \multirow{2}{*}{24\%} & & \\ 
			& & & 42.5 - 47.5 \degree N & & & \\ 
			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 2.5 - 15.0 \degree E & \multirow{2}{*}{22\%} & & \\ 
			& & & 40.0 - 50.0 \degree N & & & \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:params_GA_4Zo}
\end{table}

\begin{table}[htb]
	\caption{Pressure levels ($\sim$) automatically selected for the 4Zo method at the different subregions. R represents the reference method (Table \ref{table:params_R1}).}
	\footnotesize
	\begin{center}
		\begin{tabular}{ccccccccc}
			\hline ID & 300 & 400 & 500 & 600 & 700 & 850 & 925 & 1000 \\ 
			\hline 
			1  & $\sim$ &   &   &   & $\sim$ &   &   & $\sim \sim$ \\
			2  & $\sim$ &   &   &   & $\sim$ &   &   & $\sim \sim$ \\
			3  & $\sim$ &   &   &   & $\sim$ &   &   & $\sim \sim$ \\
			4  & $\sim$ &   &   &   & $\sim$ &   &   & $\sim \sim$ \\
			5  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
			6  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
			7  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
			8  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
			9  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
			10 &   &   &   & $\sim$ & $\sim$ &   &   & $\sim \sim$ \\
			\hline 	
			R  &   &   & $\sim$ &   &   &   &   & $\sim$ \\
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:levels_GA_4Zo}
\end{table}

\begin{table}[htb]
	\caption{CRPSS score (\%) of the three optimized methods (4Zo is the atmospheric circulation analogy detailed in the present section; 4Zo-2MIo and 4Zo-4MIo add a second level of analogy on moisture indexes, as explained in section \ref{sec:optim_moisture}).}
	\footnotesize
	\begin{center}
		\begin{tabular}{ccccccc}
			\hline 
			ID & \multicolumn{2}{c}{4Zo} & \multicolumn{2}{c}{4Zo-2MIo} & \multicolumn{2}{c}{4Zo-4MIo} \\ 
			& CP & VP & CP & VP & CP & VP \\ 
			\hline 
			1 & 40.3 & 38.5 & 45.5 & 43.8 & 45.9 & 43.6 \\
			2 & 37.8 & 34.9 & 42.4 & 40.8 & 42.9 & 41.3 \\
			3 & 36.6 & 33.9 & 41.4 & 39.0 & 41.8 & 39.5 \\
			4 & 31.2 & 30.8 & 36.1 & 36.4 & 36.8 & 37.1 \\
			5 & 34.4 & 36.5 & 38.6 & 41.4 & 39.2 & 41.8 \\
			6 & 37.0 & 39.9 & 41.0 & 44.5 & 41.9 & 44.6 \\
			7 & 30.0 & 30.1 & 33.8 & 34.6 & 34.4 & 34.8 \\
			8 & 37.7 & 40.1 & 40.7 & 43.1 & 41.2 & 43.3 \\
			9 & 33.1 & 30.0 & 38.4 & 36.6 & 38.7 & 36.3 \\
			10 & 40.0 & 40.0 & 42.6 & 42.9 & 43.3 & 43.2 \\
			\hline
			av. & 35.8 & 35.5 & 40.1 & 40.3 & 40.6 & 40.5 \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:scores}
\end{table}

\begin{table}[htb]
	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized 4Zo method.}
	\footnotesize
	\begin{center}
		\begin{tabular}{ccccccc}
			\hline 
			ID & \multicolumn{2}{c}{P\(\geq\)1 mm} & \multicolumn{2}{c}{P\(\geq\)0.1\(\cdot\)P10} & \multicolumn{2}{c}{P\(\geq\)0.5\(\cdot\)P10} \\ 
			& CP & VP & CP & VP & CP & VP \\ 
			\hline 
			1 & 10.2 & 9.4 & 8.5 & 7.9 & 17.0 & 14.2 \\ 
			2 & 9.9 & 3.4 & 10.2 & 7.3 & 19.3 & 13.7 \\ 
			3 & 13.3 & 10.5 & 13.3 & 10.9 & 19.7 & 9.7 \\ 
			4 & 11.0 & 7.4 & 12.9 & 10.0 & 23.2 & 23.8 \\ 
			5 & 8.6 & 4.2 & 10.9 & 6.2 & 25.2 & 23.8 \\ 
			6 & 10.5 & 5.1 & 11.1 & 7.1 & 21.2 & 41.1 \\ 
			7 & 24.3 & 12.4 & 33.1 & 26.0 & 71.2 & 104.3 \\ 
			8 & 19.0 & 12.7 & 26.2 & 19.2 & 39.4 & 34.9 \\ 
			9 & 12.4 & 6.8 & 13.8 & 9.9 & 24.9 & 48.1 \\ 
			10 & 13.6 & 6.8 & 14.4 & 6.9 & 29.9 & 31.5 \\ 
			\hline 
			av. & 13.3 & 7.9 & 15.4 & 11.1 & 29.1 & 34.5 \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:scores_thresholds_4Zo}
\end{table}

The resulting CRPSS scores are provided in Table \ref{table:scores} and are in average 35.8 \% for the CP and 35.5 \% for the VP. The improvement of the CRPSS score relatively to the reference method on the atmospheric circulation (optimized by the sequential procedure) is illustrated in Figure \ref{fig:figure_dcrpss_4Zo} and is in average 15.3 \% for the CP and 9.9 \% for the VP. The score was also calculated for three precipitation thresholds: P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10, P10 being the daily precipitation with a 10~year return period (Table \ref{table:scores_thresholds_4Zo}). The gain in score increases with the precipitation threshold: the relative improvement of the CRPSS is in average, respectively for the different thresholds, 13.3\%, 15.4\% and 29.1\% for the CP and 7.9\%, 11.1\% and 34.5\% for the VP. The optimization improves thus even more the forecasts for days with significant precipitation than usual days.

@@

The automatic selections of the pressure levels (Table \ref{table:levels_GA_4Zo}) and the temporal windows (not shown) for the analogy of circulation show a great homogeneity and are spatially consistent. First of all, the level 1000~hPa is always selected twice (the first time at 6 or 12~h, and the second always at 30~h) and the 700~hPa is selected once for every subregion (always at 24~h). The level which varies from one subregion to another is the upper level (however always at 12~h), which is 300~hPa for the North-West part of the catchment, 500~hPa for most of the subregions, and 600~hPa for the Conches Valley. Its spatial distribution is however homogeneous. The optimizer thus provided consistent selections of pressure levels and temporal windows, which depicts a significant preference in the AM, and the success of GAs to provide consistent results. The automatic selection of the pressure levels is a big advantage in favor of a global optimization, as it is not possible to assess all combinations of 4 levels with the sequential calibration procedure.

The resulting spatial windows (Figure \ref{fig:spatial_windows_4Zo}) may look very diverse first, but there are significant similarities for subregions located within the same vicinity. The first 4 subregions are characterized by a large spatial window on the upper level, whereas it becomes smaller for the other subregions. For most subregions, the second level (700~hPa) is represented by thin and longitudinally extended domains. The third level (1000~hPa at 6 or 12~h) also contains longitudinally extended domains, but a bit larger. The last one (1000~hPa at 30~h) is rather large and squared. Subregions number 5 (Left side valleys) and 6 (Southern ridges) have exactly the same spatial windows, which suggest that they behave in a similar way and thus could have been merged. This similarity is a good sign for the accuracy of the optimized parameters.

@@

The CRPS score was also discretized into its accuracy and sharpness components, as suggested by \citet{Bontron2004}. The changes in each of these components has been expressed relatively to the total CRPS value, of the 2Z reference method, in Figure \ref{fig:figure_dcrps_comp_4Zo} for the different regions and both the CP and the VP. One can see that the accuracy part is always improved to a greater extent than the sharpness, which can occasionally deteriorate. It means that the medians of the predicted precipitations distributions are closer to the observed value, whereas the spread of the distribution vary, but is in general a bit narrower.

The analysis of the parameters cross-compatibility shows that obviously, the parameters are optimal on the CP when they are calibrated for the given subregion (Figure \ref{fig:crossing_4Zo_calib}). However, the losses in CRPSS when exchanging the parameters are not of the same magnitude between the different subregions. Indeed, the Upper Rhone Valley (7) and moreover the Southeast ridges (8) seem to behave significantly differently. This is indeed a climatological reality, as this subregion is the most sensitive to southerly flows \citep{Horton2012}. Parameter sets from other subregions perform poorly for these subregions, and vice versa. This points at the importance of taking into account leading meteorological influences during discretization, that are not always best represented by the physical distance. Globally, the same pattern can be observed for the VP (Figure \ref{fig:crossing_4Zo_valid}), but in this case, minor improvements may be observed when crossing the parameters. The reason being that the independent VP contains other events that may be better forecasted by other parameter sets. The relatively small differences in score between parameterizations indicate that even though the parameters may differ significantly, the performance may not be drastically affected. Even a change in the pressure level does not mean a radical drop of the score value. A different parametrization may lead to a different selection of the analogue days, and thus to an improvement of the forecast under certain weather conditions at the expense of others.

@@

\begin{table}[htb]
	\caption{Parameters of the 4Zo-2MIo method (atmospheric circulation on 4 levels and moisture index on 2 levels), optimized for the Chablais subregion. Same conventions as Table \ref{table:params_GA_4Zo}.}
	\footnotesize
	\begin{center}
		\begin{tabular}{ccccccc}
			\hline L & V & H & D & W & C & N \\ 
			\hline 
			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
			\hline 
			\multirow{8}{*}{1} &  \multirow{2}{*}{Z300} & \multirow{2}{*}{12~h} & 0.0 - 15.0 \degree E & \multirow{2}{*}{23\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{74} \\
			& & & 42.5 - 55.0 \degree N & & & \\ 
			& \multirow{2}{*}{Z500} & \multirow{2}{*}{30~h} & 0.0 - 10.0 \degree E & \multirow{2}{*}{25\%} & & \\ 
			& & & 40.0 - 45.0 \degree N & & & \\ 
			& \multirow{2}{*}{Z850} & \multirow{2}{*}{12~h} & 0.0 - 10.0 \degree E & \multirow{2}{*}{26\%} & & \\ 
			& & & 42.5 - 47.5 \degree N & & & \\ 
			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 0.0 - 20.0 \degree E & \multirow{2}{*}{26\%} & & \\ 
			& & & 40.0 - 47.5 \degree N & & & \\ 
			\hline 
			\multirow{4}{*}{2} & TPW & \multirow{2}{*}{12~h} & 5.0 - 10.0 \degree E & \multirow{2}{*}{57\%} & \multirow{4}{*}{RMSE} & \multirow{4}{*}{25} \\
			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
			& TPW & \multirow{2}{*}{24~h} & 5.0 - 10.0 \degree E & \multirow{2}{*}{43\%} & & \\ 
			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:params_GA_4Zo_2MIo}
\end{table}

\begin{table}[htb]
	\caption{Atmospheric levels automatically selected for the analogy of the atmospheric circulation ($\sim$) and the analogy of moisture ($\bullet$) of the 4Zo-2MIo method, at the different subregions.  R represents the reference method (Table \ref{table:params_R2})}
	\footnotesize
	\begin{center}
		\begin{tabular}{ccccccccc}
			\hline ID & 300 & 400 & 500 & 600 & 700 & 850 & 925 & 1000 \\ 
			\hline 
			1  & $\sim$ &   & $\sim$ &   & $\bullet \bullet$  & $\sim$ &   & $\sim$ \\
			2  & $\sim$ &   &   &   & $\sim \bullet \bullet$ & $\sim$ &   & $\sim$ \\
			3  & $\sim$ &   &   &   & $\sim \bullet \bullet$ & $\sim$ & $\sim$ &   \\
			4  &   &   & $\sim$ & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
			5  &   & $\sim$ &   &   & $\sim \bullet \bullet$ &   & $\sim \sim$ &   \\
			6  &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
			7  &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
			8  &   &   & $\sim$ & $\bullet$ & $\sim \bullet$ &   & $\sim \sim$ &   \\
			9  &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ & $\sim$ &   \\
			10 &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
			\hline 
			R &   &   & $\sim$ &   &   & $\bullet \bullet$ &   & $\sim$ \\
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:levels_GA_4Zo_2MIo}
\end{table}

\begin{table}[htb]
	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized 4Zo-2MIo method.}
	\footnotesize
	\begin{center}
		\begin{tabular}{ccccccc}
			\hline 
			ID & \multicolumn{2}{c}{P\(\geq\)1 mm} & \multicolumn{2}{c}{P\(\geq\)0.1\(\cdot\)P10} & \multicolumn{2}{c}{P\(\geq\)0.5\(\cdot\)P10} \\  
			& CP & VP & CP & VP & CP & VP \\ 
			\hline 
			1 & 12.6 & 9.3 & 12.4 & 9.7 & 15.8 & 11.0 \\
			2 & 10.4 & 7.7 & 11.2 & 10.5 & 18.9 & 16.6 \\ 
			3 & 14.5 & 11.6 & 14.1 & 11.4 & 18.7 & 14.6 \\ 
			4 & 11.4 & 9.4 & 11.5 & 11.6 & 14.9 & 22.7 \\ 
			5 & 11.8 & 8.0 & 12.2 & 8.9 & 12.0 & 12.8 \\ 
			6 & 11.3 & 7.1 & 11.2 & 8.0 & 15.3 & 29.1 \\ 
			7 & 20.5 & 15.5 & 25.2 & 24.0 & 43.0 & 79.5 \\
			8 & 19.3 & 15.7 & 23.1 & 18.6 & 25.2 & 31.7 \\ 
			9 & 17.0 & 15.4 & 17.4 & 16.5 & 23.7 & 39.4 \\ 
			10 & 12.9 & 9.6 & 13.8 & 11.1 & 28.5 & 32.1 \\ 
			\hline 
			av. & 14.2 & 10.9 & 15.2 & 13.0 & 21.6 & 28.9 \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:scores_thresholds_4Zo-2MIo}
\end{table}

@@

As for 4Zo, the 4Zo-2MIo and 4Zo-4MIo methods present larger improvements in the forecast for significant rainfall (thresholds P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10). The improvement are relatively similar for 4Zo-2MIo (Table \ref{table:scores_thresholds_4Zo-2MIo}) and 4Zo-4MIo (not shown), with slightly superior scores for the latter on small precipitation (P\(\geq\)1 mm : 17.7\% and 13.0\%) and extremes (P\(\geq\)0.5\(\cdot\)P10 : 23.7\% and 29.2\%).

@@

When optimizing a method made of 2 levels of analogy, the introduction of moisture variables in the second level has an influence on the parameter values of the first level. This is first visible on number $N_{1}$ of analogues to be selected on the first level, and on the selection of the pressure levels for the circulation analogy. As for the sequential procedure, the optimal value of $N_{1}$ increases when adding a second level of analogy (Figure \ref{fig:figure_nb_analogues}). One can also notice that the optimal number of analogues $N_{2}$ for the second level of analogy of 4Zo-2MIo is slightly inferior to $N_{1}$ from 4Zo, but very close. There is a relationship between the optimal values of $N_{1}$ from both methods: the higher the $N_{1}$ of the first method, the higher $N_{1}$ and $N_{2}$ of the second is (Figure \ref{fig:figure_nb_analogues_relationships}). This relationship is not to be considered perfectly robust and should not be transposed to another case study, but in this case, it relates the magnitudes of the numbers on the various levels and methods. The optimal final number of analogues do not vary much: $23 \leq N_{1} \leq 33$ for 4Zo and $21 \leq N_{2} \leq 28$ for 4Zo-2MIo. However, the optimal number of $N_{1}$ analogues of the first level of 4Zo-2MIo varies to a greater extent: $48 \leq N_{1} \leq 84$. In this latter method, it may be problematic to consider a fixed and unique value for all regions.

As for the pressure levels, the 1000~hPa that was previously systematically selected twice (Table \ref{table:levels_GA_4Zo}) is now less chosen (once or even not at all) for both 4Zo-2MIo (Table \ref{table:levels_GA_4Zo_2MIo}) and 4Zo-4MIo (not shown). There is indeed a shift of the previously selected 1000~hPa for higher levels, which is even slightly stronger with 4 moisture predictors than with 2. This change is likely due to the fact that when considering only the circulation analogy, the method tries to take into account information that can serve as proxy for moisture assessment, whereas it does not need it with the moisture index. This aspect has never been demonstrated before, as sequential calibration tools do not allow it. It can only be assessed by a global optimization technique that can tune jointly both levels of analogy.

>>>>

\begin{abstract}
The analogue method is often used to forecast precipitation based on predictors variables provided by global models. The method samples a selection of days in the archives that are similar to the target day to predict, and consider the set of their corresponding observed precipitation (the predictand) as the conditional distribution for the target day. The relationship between predictors and predictands relies on some parameters that characterize how and where the similitude between two atmospheric situations is defined.

@@

With the perspective to overcome these limitations, a global optimization by Genetic Algorithms (GAs) was introduced by \citet{Horton2016a}. An intensive assessment work resulted in recommendations of parametrization of GAs in order to optimize AMs successfully. The present paper is based on these recommendations and illustrate them on precipitation predicting for the upper Rh\^{o}ne catchment in the Swiss Alps. It aims at proving the relevance of a fully-automatic, objective, and global, optimization technique for AMs. The applications are indeed numerous, as the AM has to be adapted to every new location it is applied, or to any new predictand it should predict.

@@

@@

@@

The AM relies on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series one wants to predict.

@@

The score that is most often used to assess an AM performance is the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}. It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analogue situations, compared to the observed value $y^{0}$. The better the prediction, the smaller the score. The mean CRPS of a prediction series of length $n$ can be written:

@@

\begin{equation}
\label{eq:CRPSS}
CRPSS = \frac{CRPS-CRPS_{r}}{CRPS_{p}-CRPS_{r}} = 1-\frac{CRPS}{CRPS_{r}}
\end{equation}
where $CRPS_{r}$ is the CRPS value for the reference and $CRPS_{p}$ would be the one for a perfect prediction (which implies $CRPS_{p}~=~0$). A better prediction is characterized by an increase in CRPSS.

@@

The reference method for the analogy of the atmospheric circulation (2Z, Table \ref{table:params_R1}), based on Z500 and Z1000, was first considered. The optimizer had to choose the number of analogues, both spatial windows with no overlapping constraint, as well as the temporal windows (hours of observation of the geopotential), what the sequential calibration cannot do. With these degrees of freedom, a relative CRPSS improvement of 3.97\% and 2.45\% in average was obtained for the CP and the VP respectively. Some tests showed that most of the gains are due to the non-overlapping spatial windows. This is not a tremendous improvement, but it demonstrated that the optimizer was able to get relevant parameters.

Then, an additional degree of freedom was provided to the GAs by letting them choose the pressure levels along with the other parameters, which is also a non-automated process in the sequential calibration. This degree of freedom increased the optimization time and may decrease the number of simulations that converge to a single solution. However, most solutions were very close in terms of score. The averaged relative improvement of the CRPSS is 5.63\% for the CP and 3.82\% for the VP. The pressure levels that were chosen are Z500 or Z700 for the upper level, and Z925 or Z1000 (most often) for the lower level.

Parallel analyses showed that the analogy of circulation is incomplete, and that the geopotential still contains relevant information that can improve the statistical relationship. Therefore, a third predictor was added (still on the geopotential height) that the optimizer could use along with the previous parameters. There was no constraint on the predictors, so that the same pressure level could be selected more than once. Some improvements were found on the score, both for the CP and the VP, confirming that this additional information is beneficial for the quality of the prediction. We then tried with 4 predictors, and so on, up to 8. Every time a new predictor to optimize was added, the score on the CP increased, but always more to a smaller extent. However, the score value on the VP dropped after 4 predictors, revealing an over-parametrization of the method, and thus a lack of robustness. Considering 4 predictors is optimal for this case study, since the gain in CRPSS is significant. It cannot be excluded that another number would prevail in another region under other meteorological conditions.

@@

The resulting CRPSS scores are provided in Table \ref{table:scores} and are in average 35.8 \% for the CP and 35.5 \% for the VP. The improvement of the CRPSS score relatively to the reference method on the atmospheric circulation (optimized by the sequential procedure) is illustrated in Figure \ref{fig:figure_dcrpss_4Zo} and is in average 15.3 \% for the CP and 9.9 \% for the VP. The score was also calculated for three precipitation thresholds: P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10, P10 being the daily precipitation with a 10~year return period (Table \ref{table:scores_thresholds_4Zo}). The gain in score increases with the precipitation threshold: the relative improvement of the CRPSS is in average, respectively for the different thresholds, 13.3\%, 15.4\% and 29.1\% for the CP and 7.9\%, 11.1\% and 34.5\% for the VP. The optimization improves thus even more the prediction for days with significant precipitation than usual days.

@@

The automatic selections of the pressure levels (Table \ref{table:levels_GA_4Zo}) and the temporal windows (not shown) for the analogy of circulation show a great homogeneity and are spatially consistent. First of all, the level Z1000 is always selected twice (the first time at 6 or 12~h, and the second always at 30~h) and Z700 is selected once for every subregion (always at 24~h). The level which varies from one subregion to another is the upper level (however always at 12~h), which is Z300 for the North-West part of the catchment, Z500 for most of the subregions, and Z600 for the Conches Valley. Its spatial distribution is however homogeneous. The optimizer thus provided consistent selections of pressure levels and temporal windows, which depicts a significant preference in the AM, and the success of GAs to provide consistent results. The automatic selection of the pressure levels is a big advantage in favor of a global optimization.

The resulting spatial windows (Figure \ref{fig:spatial_windows_4Zo}) may look very diverse first, but there are significant similarities for subregions located within the same vicinity. The first 4 subregions are characterized by a large spatial window on the upper level, whereas it is smaller elsewhere. For most subregions, the second level (Z700) is represented by thin and longitudinally extended domains. The third level (Z1000 at 6 or 12~h) also contains longitudinally extended domains, but a bit larger. The last one (Z1000 at 30~h) is rather large and squared. Subregions number 5 (Left side valleys) and 6 (Southern ridges) have exactly the same spatial windows, which suggest that they behave in a similar way and thus could have been merged. This similarity is a good sign for the accuracy of the optimized parameters.

@@

The CRPS score was also discretized into its accuracy and sharpness components, as suggested by \citet{Bontron2004}. The changes in each of these components has been illustrated in Figure \ref{fig:figure_dcrps_comp_4Zo} relatively to the total CRPS value of the 2Z reference method for the different regions and both the CP and the VP. One can see that the accuracy part is always improved to a greater extent than the sharpness, which can occasionally deteriorate. It means that the medians of the predicted precipitations distributions are closer to the observed value, whereas the spread of the distribution vary, but is in general a bit narrower.

The analysis of the parameters cross-compatibility shows that obviously, the parameters are optimal on the CP when they are optimized for a given subregion (Figure \ref{fig:crossing_4Zo_calib}). However, the losses in CRPSS when exchanging the parameters are not of the same magnitude between the different subregions. Indeed, the Upper Rhone Valley (7) and moreover the Southeast ridges (8) seem to behave significantly differently, likely due to their particular sensitivity to southerly flows \citep{Horton2012}. This points at the importance of taking into account leading meteorological influences during discretization, that are not always best represented by the physical distance. Globally, the same pattern can be observed for the VP (Figure \ref{fig:crossing_4Zo_valid}), but in this case, minor improvements may occur when crossing the parameters, due to the presence of other events in the VP that may be better predicted by a different parameter set. The relatively small gaps in score between parameterizations indicate that even though the parameters may differ significantly, the performance may not be drastically affected. Even a change in the pressure level does not mean a radical drop of the score value. A different parametrization may lead to a distinct selection of analogue days, and thus to an improvement of the prediction under certain weather conditions at the expense of others.

@@

@@

As for 4Zo, the 4Zo-2MIo and 4Zo-4MIo methods present larger improvements in the prediction for significant rainfall (thresholds P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10). The improvement are relatively similar for 4Zo-2MIo (Table \ref{table:scores_thresholds_4Zo-2MIo}) and 4Zo-4MIo (not shown), with slightly superior scores for the latter on small precipitation (P\(\geq\)1 mm : 17.7\% and 13.0\%) and extremes (P\(\geq\)0.5\(\cdot\)P10 : 23.7\% and 29.2\%).

@@

When optimizing a method made of 2 levels of analogy, the introduction of moisture variables in the second level has an influence on the parameter values of the first level. This is first visible on the number $N_{1}$ of analogues to be selected on the first level, and on the selection of the pressure levels for the circulation analogy.

As for the sequential procedure, the optimal value of $N_{1}$ increases when adding a second level of analogy (Figure \ref{fig:figure_nb_analogues}). One can also notice that the optimal number of analogues $N_{2}$ for the second level of analogy of 4Zo-2MIo is slightly inferior to $N_{1}$ from 4Zo, but very close. There is a trend between the optimal analogue number values of both methods: the higher $N_{1}$ of the 4Zo method, the higher $N_{1}$ and $N_{2}$ of 4Zo-2MIo is (Figure \ref{fig:figure_nb_analogues_relationships}). This relationship is not to be considered perfectly robust and should not be transposed to another case study, but in this case, it relates the magnitudes of the $N_{1}$ and $N_{2}$ on the various levels and methods.

The optimal final number of analogues do not vary much: $23 \leq N_{1} \leq 33$ for 4Zo and $21 \leq N_{2} \leq 28$ for 4Zo-2MIo. However, the optimal number of $N_{1}$ analogues of the first level of 4Zo-2MIo varies to a greater extent: $48 \leq N_{1} \leq 84$. In this latter method, it may be problematic to consider a fixed and unique value for all regions.

As for the pressure levels, Z1000 that was previously systematically selected twice (Table \ref{table:levels_GA_4Zo}) is now less chosen (once or even not at all) for both 4Zo-2MIo (Table \ref{table:levels_GA_4Zo_2MIo}) and 4Zo-4MIo (not shown). There is indeed a shift of the previously selected Z1000 for higher levels, that is even slightly stronger with 4 moisture predictors than with 2. This change is likely due to the fact that when considering only the circulation analogy, the method tries to take into account information that can serve as proxy for moisture assessment, whereas it does not need it with the moisture index. This aspect has never been demonstrated before, as sequential calibration tools do not allow it. It can only be assessed by a global optimization technique that can tune jointly both levels of analogy.
